---
title: "Ventura River Discharge"
author: "Grace Lewin"
date: "10/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dataRetrieval)
library(tidyverse)
library(kableExtra)
```


```{r}
siteNumber <- "11118500"
parameterCd <- "00060" # discharge
startDate <- "2019-10-01"
endDate <- "2020-10-05"

#siteNumber_SP <- '11113500'
discharge <- readNWISdata(sites=siteNumber, service="iv", 
                   parameterCd="00060", 
                   startDate=startDate,endDate=endDate,
                   tz="America/Los_Angeles")


ggplot(discharge, aes(x = dateTime, y = X_00060_00000)) +
  geom_line(aes(color = site_no)) +
  scale_color_discrete(name = "Site", labels = "Ventura") +
  theme_minimal() +
  labs(title = "Discharge of the Ventura Creek",
       subtitle = "Oct. 1, 2019 - Oct. 5, 2020",
       x = "Date",
       y = "Discharge (ft^3/s)")
```


```{r}
siteNumber1 <- c("11118500", '11113500')
parameterCd <- "00060" # discharge
startDate <- "2021-10-04T18:00Z"
endDate <- "2021-10-06T00:00Z"

#siteNumber_SP <- '11113500'
discharge1 <- readNWISdata(sites=siteNumber1, service="iv", 
                   parameterCd="00060", 
                   startDate=startDate,endDate=endDate,
                   tz="America/Los_Angeles")


ggplot(discharge1, aes(x = dateTime, y = X_00060_00000)) +
  geom_line(aes(color = site_no)) +
  scale_color_discrete(name = "Site", labels = (c("Santa Paula", "Ventura"))) +
  theme_minimal() +
  labs(title = "Discharge of the Ventura and Santa Paula Creek",
       subtitle = "Oct. 4 - 6 2021",
       x = "Date",
       y = "Discharge (ft^3/s)")

#peak Santa Paula flow
peak_SP <- discharge1 %>% 
  filter(site_no == '11113500') %>% 
  filter(X_00060_00000 == max(X_00060_00000)) %>% 
  select(dateTime, X_00060_00000)

#peak Ventura flow
peak_V <- discharge1 %>% 
  filter(site_no == '11118500') %>% 
  filter(X_00060_00000 == max(X_00060_00000)) %>% 
  select(dateTime, X_00060_00000)
```


2. The best way I found to query multiple sites using this R package is to put the different site numbers into a concatenated list (using `c()`) labeled `siteNumber`. Then, you can call `site = siteNumber` in the `readNWISdata()` function, and it will give you the data for all of the site numbers you inputted into that list.  

3. See above plot showing the stream flow in the Ventura and Santa Paula creeks for October 4-6. We can see from this plot and the tables below that the Santa Paula stream flow peaked on Oct. 5th at about from 3:30am - 4:15am. In the Ventura creek, there was a slight peak from about 12:25am - 10:25am. 

```{r}
kable(peak_SP, col.names = c("Date and Time", "Flow"))

kable(peak_V, col.names = c("Date and Time", "Flow"))
```


